An algorithm for searching the global minimum of univariate discontinuous functions\thanks{This work was supported by project no. 0729-2020-0055.}

### 2020-12-16 2021/ICCS_BarkalovUsova/iccs.tex
added actual results

Let us illustrate the operation of the algorithm when searching for the minimum of the function
\begin{equation}\label{testFunction}
\varphi(x) =  0.1\sum_{i=1}^5{i\sin{(10(i+1)x+i)}}+
\begin{cases}
	-4, &0 \leq x < 3.1\\
	10, &3.1 \leq x < 4.6\\
	0, &4.6 \leq x < 7.0\\
	30, &7.0 \leq x < 9.0\\
	0, &9.0 \leq x \leq 10.0
\end{cases}
\end{equation}
at $x\in[0,10]$. All discontinuity points were considered known, the parameters of the method $r=2.0,\epsilon=0.001$ were used. Fig.~\ref{ris1} shows a graph of this function, the discontinuities are marked with a dotted line. The dashes under the graph indicate the points of 74 trials required for the algorithm to solve problem with the specified accuracy.

@@

Fig.~\ref{ris2} shows the results of solving the problem from the previous example (\ref{testFunction}), in which the discontinuity points were considered unspecified. Here we used the parameters of the method $r=2.0, \epsilon=0.001, Q=3.0, q=0.3$. The dashes under the graph indicate the points of 140 trials required for the algorithm to solve problems with the specified accuracy.

>>>>

Let us illustrate the operation of the algorithm when searching for the minimum of the function
\begin{equation}\label{testFunction}
\varphi(x) =  0.1\sum_{i=1}^5{i\sin{(10(i+1)x+i)}}+
\begin{cases}
	-4, &0 \leq x < 3.1\\
	10, &3.1 \leq x < 4.6\\
	0, &4.6 \leq x < 7.0\\
	30, &7.0 \leq x < 9.0\\
	0, &9.0 \leq x \leq 10.0
\end{cases}
\end{equation}
at $x\in[0,10]$. All discontinuity points were considered known, the parameters of the method $r=2.0,\epsilon=0.001$ were used. Fig.~\ref{ris1} shows a graph of this function, the discontinuities are marked with a dotted line. The dashes under the graph indicate the points of 70 trials required for the algorithm to solve problem with the specified accuracy.

@@

Fig.~\ref{ris2} shows the results of solving the problem from the previous example (\ref{testFunction}), in which the discontinuity points were considered unspecified. Here we used the parameters of the method $r=2.0, \epsilon=0.001, Q=3.0, q=0.3$. The dashes under the graph indicate the points of 70 trials required for the algorithm to solve problems with the specified accuracy.
